MATH/COMP 562 ASSIGNMENT 3

### 2023-06-25 assignment-3/article.tex
Solve last 2 problems

      Subtracting $g(w_1, S_1)$ from both sides of the inequality, and then multiplying both sides by 2 gives the first desired inequality:
      $$\frac{\lambda}{2}||w_1-w_2||^2 \leq g(w_2,S_1)-g(w_1, S_1)$$
      We can obtain the other inequality by the same argument, or via symmetry.
      $$\frac{\lambda}{2}||w_1-w_2||^2 \leq g(w_1,S_2)-g(w_2, S_2)$$
    \item We start by rewriting the inequalities from the preceding exercise.
      \begin{align*}
        \frac{\lambda}{2}||w_1-w_2||^2 \leq g(w_2, z_1)-g(w_1, z_1) \\
        \frac{\lambda}{2}||w_1-w_2||^2 \leq g(w_1, z_2)-g(w_2, z_2)
      \end{align*}
      Then we add both inequalities together to obtain:
      \begin{align*}
        \lambda ||w_1-w_2||^2 &\leq (g(w_2,z_1)-g(w_1,z_1)+g(w_1,z_2)-g(w_2,z_2)) \\
        \hphantom{\lambda ||w_1-w_2||^2} &\leq (f(w_2,z_1) + ||w_2||^2 -f(w_1,z_1) - ||w_2||^2 \\
        \hphantom{\lambda ||w_1-w_2||^2}&+f(w_1,z_2) + ||w_1||^2-f(w_2,z_2) - ||w_1||^2 \\
        &\leq f(w_2,z_1)-f(w_1,z_1)+f(w_1,z_2)-f(w_2,z_2) \\
        &\leq \frac{1}{m} (\ell(w_2,z_1)-\ell(w_1,z_1)+\ell(w_1,z_2)-\ell(w_2,z_2))
      \end{align*}
      where the last inequality comes from the fact that $f(w_i,S_i) = \frac{1}{m}\ell(w_i, z_i)$.
      \item We begin by calculating an upper bound for $\ell(w,z)$: \begin{align*}
        \ell(w, z) &= (w \cdot x - y)^2 \\
        &= ||w\cdot x||^2 - 2 (w \cdot x) \cdot y + ||y||^2 \\
        &\leq ||w||^2 ||x||^2 - 2||w|| ||x|| ||y|| + ||y||^2 \\
        &\leq ||w||^2 ||x||^2 + ||y||^2 \\
        &\leq C_w^2C_x^2 + C_y^2
        \end{align*}

        Now we use the hint:
        \begin{align*}
          \ell(w_2,z_1) - \ell(w_1,z_1) &= (w_2\cdot x - y)^2 - (w_1\cdot x - y)^2 \\
          \hphantom{\ell(w_2,z_1) - \ell(w_1,z_1)} &= (w_2\cdot x - y - w_1\cdot x + y)(w_2\cdot x - y + w_1\cdot x - y) \\
          \hphantom{\ell(w_2,z_1) - \ell(w_1,z_1)} &= ((w_2 - w_1)\cdot x)((w_1 + w_2)\cdot x - 2y)
        \end{align*}
  \end{enumerate}
\end{solution}

>>>>

      Subtracting $g(w_1, S_1)$ from both sides of the inequality, and then multiplying both sides by 2 gives the first desired inequality:
      $$\frac{\lambda}{2}||w_1-w_2||^2 \leq g(w_2,S_1)-g(w_1, S_1)$$
      We can obtain the other inequality by the same argument, or via symmetry.
      $$\frac{\lambda}{2}||w_1-w_2||^2 \leq g(w_1,S_2)-g(w_2, S_2)$$
    \item We start by rewriting the inequalities from the preceding exercise.
      \begin{align*}
        \frac{\lambda}{2}||w_1-w_2||^2 \leq g(w_2, z_1)-g(w_1, z_1) \\
        \frac{\lambda}{2}||w_1-w_2||^2 \leq g(w_1, z_2)-g(w_2, z_2)
      \end{align*}
      Then we add both inequalities together to obtain:
      \begin{align*}
        \lambda ||w_1-w_2||^2 &\leq (g(w_2,z_1)-g(w_1,z_1)+g(w_1,z_2)-g(w_2,z_2)) \\
        \hphantom{\lambda ||w_1-w_2||^2} &\leq (f(w_2,z_1) + ||w_2||^2 -f(w_1,z_1) - ||w_2||^2 \\
        \hphantom{\lambda ||w_1-w_2||^2}&+f(w_1,z_2) + ||w_1||^2-f(w_2,z_2) - ||w_1||^2 \\
        &\leq f(w_2,z_1)-f(w_1,z_1)+f(w_1,z_2)-f(w_2,z_2) \\
        &\leq \frac{1}{m} (\ell(w_2,z_1)-\ell(w_1,z_1)+\ell(w_1,z_2)-\ell(w_2,z_2))
      \end{align*}
      where the last inequality comes from the fact that $f(w_i,S_i) = \frac{1}{m}\ell(w_i, z_i)$.
    \item We begin by applying the hint with $\ell(w_2,z_1) - \ell(w_1,z_1)$:
        \begin{align*}
          \ell(w_2,z_1) - \ell(w_1,z_1) &= (w_2\cdot x - y)^2 - (w_1\cdot x - y)^2 \\
          \hphantom{\ell(w_2,z_1) - \ell(w_1,z_1)} &= (w_2\cdot x - y - w_1\cdot x + y)(w_2\cdot x - y + w_1\cdot x - y) \\
          \hphantom{\ell(w_2,z_1) - \ell(w_1,z_1)} &= ((w_2 - w_1)\cdot x)((w_1 + w_2)\cdot x - 2y) \\
          \hphantom{\ell(w_2,z_1) - \ell(w_1,z_1)} &\leq (2C_wC_x)(2C_wC_x+2C_y) \\
          \hphantom{\ell(w_2,z_1) - \ell(w_1,z_1)} &\leq 2C_wC_x(C_wC_x + C_y)
        \end{align*}
        Now we can apply the triangle inequality to the right hand side of the inequality from the previous exercise, and then we will apply our upper bound.
        \begin{align*}
          &\hphantom{\leq} \frac{1}{m} |\ell(w_2,z_1)-\ell(w_1,z_1)+\ell(w_1,z_2)-\ell(w_2,z_2)| \\
          &\leq \frac{1}{m} |\ell(w_2,z_1)-\ell(w_1,z_1)| + \frac{1}{m}|\ell(w_1,z_2)-\ell(w_2,z_2)| \\
          &\leq \frac{4C_wC_x(C_wC_x + C_y)}{m}
        \end{align*}
      \item Since $L(A(Z_1)) - L(A(Z_2))$ can be bounded by function of $m$, the Ridge Regression problem is replace-one-stable (ROS).

        The ROS rate, denoted $\beta(m)$ is given by the following:
        \[
        \begin{aligned}[t]
        L(A(Z_1))-L(A(Z_2)) &= \frac{1}{m} |\ell(w_2,z_1)-\ell(w_1,z_1)+\ell(w_1,z_2)-\ell(w_2,z_2)| \\
        &\leq \frac{4C_wC_x(C_wC_x + C_y)}{m} = \beta(m)
        \end{aligned}
        \]
  \end{enumerate}
\end{solution}
